\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-13 papers/jss/article.Rnw
sync
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@763 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\Sexpr{m} data sets could be converted to Protocol Buffers
(\Sexpr{format(100*m/n,digits=1)}\%).  The next section illustrates how
many bytes were used to store the data sets under four different
situations:
\begin{itemize}
\item normal R serialization,
\item R serialization followed by gzip,
\item normal Protocol Buffer serialization, and
\item Protocol Buffer serialization followed by gzip.
\end{itemize}

@@

>>>>

\Sexpr{m} data sets can be converted to Protocol Buffers
(\Sexpr{format(100*m/n,digits=1)}\%) without loss of information. Upon closer
inspection, all other datasets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes used by the \pkg{nlme} package, among which a \emph{formula} object.
Because formulas are R \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize_pb} is used on objects of this class (or other objects
containing unsupported data types), it will serialize all other values and 
attributes of the object, but skip over the unsupported types with a warning.

@@

This section compares how many bytes are used to store data sets
using four different methods:

\begin{itemize}
\item normal R serialization,
\item R serialization followed by gzip,
\item normal Protocol Buffer serialization, and
\item Protocol Buffer serialization followed by gzip.
\end{itemize}
